%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.
    % The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{twentysecondcv}

    % For mathematical symbols
\usepackage{amsmath}

  
    % Set applicant's personal data for header
    \name{Manish Nehara}
   \address {+91-9177592030 \linebreak Bengaluru, KA }
    \contacts{mknehra38@gmail.com \linebreak www.linkedin.com/in/manishnehara}
  

\begin{document}
% Print the header
\makeheader
\begin{cvsection}{Experience}
    
    
	\begin{cvsubsection}{Senior Software Engineer}{Verifone}{May 2019 - present}
		            
		
		    Was responsible for successfully completing "\textbf{Entity Service}" project, which provides a common Application to store and retrieve \textbf{Merchant on-boarding data}. Entity Service stores merchant details in a graph database (\textbf{RedisGraph}) with the help of rationalized hierarchical structure defined.
    
	\begin{itemize}%
	        \item \textbf{Security Token Service:} Designed service for Security with \textbf{JWT Authentication}. User will get a valid JSON Web Token with role permissions and then allow the user access to the api only if it has a valid token and api-level permission.
		    \item \textbf{Merhcant Services:} Designed and developed loosly coupled \textbf{Microservices} to store merchant data and their user's profiles and credentials data in hierarchical structure.
		     \item \textbf{Sync Service:} Designed and developed Sync Service using \textbf{kafka} to keep the merchant data back-up by synchronizing data b/w different data centers.
		       \item \textbf{Messaging Service:} Developed MicroServices to send relevant user data to alert users in case if their password is going to expire or if it is already expired.
     \item \textbf{IDM-User Management:} Designed and Integrated Entity Service with IDM for ensuring that the right users have the appropriate access to technology resources.
     \item \textbf{AGILE :}  Working in agile methodology and familiar with Jira, Bitbucket, IJ, SourceTree, git.
 
	\end{itemize}
	\end{cvsubsection}
	\begin{cvsubsection}{Software Engineer}{CGI Group}{Aug, 2017 - May, 2019}
		\begin{itemize}%
		\item \textbf{ABI:} Improved performance of existing tool which was used to map internal data with thried party services.
		\item Desinged and 	Developed \textbf{Rest-Apis} for existing project.
		\item \textbf{Full-Stack Developer - StackRoute: } Designed and developed  \textbf{WorkFlow Engine} from scratch till deployment. 
			\begin{itemize}%
			\item \textbf{Distributed Workflow Engine : }Contributed to the development of distributed workflow engine (equivalent 
to \textbf{CI-CD}). The engine could be configured to automate a set of tasks 
e.g. git push, clone or sending a message on twitter, simple tasks.
	\end{itemize}
		
		\end{itemize}
	\end{cvsubsection}
\end{cvsection}
\begin{cvsection}{Education}
	\begin{cvsubsection}{Warangal}{National Institute of Technology}{Aug, 2013-May, 2017}
		\begin{itemize}
			\item \textbf{B.Tech, Computer Science and Engineering}.
		\end{itemize}
	\end{cvsubsection}
\end{cvsection}

\begin{cvsection}{Technical Skills}
	\begin{cvsubsection}{}{}{}
		\begin{itemize}
			\item \textbf{Programming languages:}  C, C++, Java, Python(beginner), SQL, HTML ,CSS 5, Angular 4, React(beginner)
			\item \textbf{Databases:} RedisGraph, MySQL, MongoDB, Neo4j
			\item \textbf{Frameworks/Tools:} Spring Boot, Django(beginner), , Kafka, JMeter, Kibana, AppDynamis, MobaXtream, Cloud Services(beginner)  
			\item \textbf{Operating systems:}  Ubuntu, Windows 
		 
		\end{itemize}
	\end{cvsubsection}
\end{cvsection}
% \begin{cvsection}{Projects}
% 	\begin{cvsubsection}{}{}{}
% 		\begin{itemize}
% 			\setlength\itemsep{3pt}
% 			\item \textbf{Analysis of the Performance of DNA Sequence Compression Algorithms} Developed an algorithm to analyze the performance between ERGC(Efficient Referential Genome Compression) algorithm and NRGC (Novel Referential Genome Compression) algorithm. Paper published in HELIX Conference (https://bit.ly/2TO2jLb).
% 			\item \textbf{P2P} Developed Web based P2P file sharing application build on data channel API.
% 		\end{itemize}
% 	\end{cvsubsection}
% \end{cvsection}
\begin{cvsection}{Honors and Achievements}
	\begin{cvsubsection}{}{}{}
		\begin{itemize}
			\setlength\itemsep{3pt} 
			\item Received \textbf{Discretionary Retention Award-2020}  for outstanding performance in Verifone.
			\item June 2016 Online Coding Competition – \textbf{14th} rank
			\item Rank \textbf{4107} out of 12 lakh candidates in JEE Main, 2013.
            
		\end{itemize}
	\end{cvsubsection}
\end{cvsection}
\end{document}